---
title: "Clustering-Exer"
author: "leanne"
date: "31/08/2019"
output: html_document
---

## Data Preprocessing

### Scaling

```{r}
## sample data set
set.seed(1410)
y <- matrix(rnorm(50), 10, 5, dimnames=list(paste("g", 1:10, sep=""), 
            paste("t", 1:5, sep="")))
dim(y)
y
```

```{r}
## Scaling
yscaled <- t(scale(t(y))) # Centers and scales y row-wise
apply(yscaled, 1, sd)
```

## Distance Matrices

### Euclidean distance matrix

```{r}
dist(y[1:4,], method = "euclidean")
```

### Correlation-based distance matrix

Correlation matrix

```{r}
c <- cor(t(y), method="pearson")
as.matrix(c)
as.matrix(c)[1:4,1:4]
```

Correlation-based distance matrix

```{r}
d <- as.dist(1-c)
as.matrix(d)[1:4,1:4]
```

### K-mean clustering with PAM

```{r}
require(cluster)
pamy <- pam(d,4)
# plot clusters
plot(d, col = pamy$clustering)
```

## Data Preprocessing

### Scaling

```{r}
require(dplyr)
## sample data set
set.seed(1410)
df <- iris %>% select(-Species)
```

```{r}
## execution
result <- pam(df,3,FALSE,"euclidean")
## print results
summary(result)
## plot clusters 
plot(df, col = result$clustering)
#add the medoids to the plot
points(result$medoids, col = 1:3, pch = 4)
```

## Distance Matrices

### Euclidean distance matrix

```{r}
dist(df[1:4,], method = "euclidean")
```

### Correlation-based distance matrix

Correlation matrix

```{r}
c <- cor(t(df), method="pearson")
#as.matrix(c)
as.matrix(c)[1:4,1:4]
```

Correlation-based distance matrix

```{r}
d <- as.dist(1-c)
as.matrix(d)[1:4,1:4]
```

### K-mean clustering with PAM

```{r}
require(cluster)
pamy <- pam(d,4)
# plot clusters
plot(d, col = pamy$clustering)

```